User-level Grid Monitoring with Inca 2

### 2007-02-26 papers/hpdc-gmw-2007/paper.tex
add other uses section
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6567 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

% Standard "Grids are good" intro paragraph.  But are complex.  
Grid systems provide unified and coherent access to distributed computing,
data storage and analysis, instruments, and other resources.  These systems
require the careful coordination of software packages, services, and
configurations across multiple, heterogeneous resources.  The TeraGrid
project~\cite{teragrid}, for example, manages the coordination of software and
services by deploying and monitoring a common user environment across
distributed, heterogeneous resources. The organization of TeraGrid software
and services is referred to as the Common TeraGrid Software and Services
(CTSS).  TeraGrid's software and services uniformity simplifies access to its
resources, which consist of more than 102 teraflops of compute capability and
more than 15 petabytes of online storage, all interconnected by a network that
can transfer a terabyte of data in under 10 minutes.

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains 
requiring a significant amount of coordination.  This is typically performed by
a group of Grid operators who take into account local site policies 
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured for the set of heterogeneous
resources.  Each site's system administrators, who are not necessarily Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise inconsistencies between the resources arise that either
inconvenience the user or prevent them from using particular resources
together.  Second, as a large distributed system, failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs.  In order to detect such problems, 
monitoring of the resources is required.

% What types of Grid monitoring are around and what the limitations are
One approach to monitoring Grids, used by tools such as
MonALISA~\cite{monalisa} and GridICE~\cite{gridice}, is to aggregate and
display data from existing cluster or system administrator monitoring tools
such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, and
Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
resources where low-level host statistics and queue information can be
examined.  This type of monitoring information is useful for showing the
utilization of Grid resources but it does not provide the type of
high-level monitoring needed to detect user problems within the Grid
infrastructure, such as incompatible software versions.

@@

% Philosophy of user-level testing
% Practical byproducts
The main goal of the Inca 2 design was to XXX (general, flexible, easy to
install, deploy, and
maintain, scalable, secure).
The following lists the key features of Inca 2 noting which are new features
to Inca 1 versus improved.

@@

\item Collects a wide variety of user-level monitoring results (e.g., simple
test data to more complex performance benchmark output).  (improved)

\item Captures the context of a test or benchmark as it executes (e.g.,
executable name, inputs, source host, etc.) so that system administrators have
enough information to understand the result and can troubleshoot system
problems without having to know the internals of Inca 2. (improved)

\item Provides facilities to ease the process of writing tests or benchmarks
and deploying them into Inca 2 installations. (improved)

\item Provides facilities for sharing tests or benchmarks with other Inca 2
users in order to promote sharing of each other's expertise (new)

\item Easily adapts to new resources and monitoring requirements in order to
facilitate maintenance of a running Inca 2 deployment. (improved)

\item Stores and archives monitoring results (especially any error messages) 
in order to understand the behavior of a Grid over time. The results
are available through a flexible querying interface. (improved)

%myproxy stuff
\item A running monitoring system should have a limited impact on the resources
it measures and should be secure.
\end{enumerate}

@@

\begin{figure*}[htb]
  \centering
  \mbox{\epsfig{file=arch.eps, width=.8\textwidth}}
  \caption{\label{arch_fig} Inca architecture.}
\end{figure*}

@@

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) an output sample.}
\end{figure}

An Inca reporter is an executable program that tests or measures some aspect
of a system or installed software.   Reporter executables are designed to be
easy to produce and can be run outside of the Inca system (e.g., by a system
administrator).  A reporter should be written following the user-level
monitoring guidelines described in the introduction and could be a simple
Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
support certain command line options and produce an XML document or report
according to the Inca reporter schema.  The goal of the reporter schema is to
accommodate multiple types of data and to capture information about the
reporter execution to diagnose any detected failures.  The reporter schema
consists of the following elements:

@@

% What are repositories and their key features
Reporter repositories are collections that consist of reporters, required
packages and libraries (including the Perl APIs described in the previous
section), and a catalog file.  Repository contents are accessible using a URL
and designed to be shared across multiple Inca deployments.  The catalog file
follows APT's Packages.gz~\cite{apt} format and thus tar.gz dependencies such
as non-standard Perl APIs or source code can be added to reporter catalog
entries.  Inca will then automatically deploy tar.gz dependencies into a
subdirectory of its installation (more in Section~\ref{agent}).  This enables
reporters to be deployed to resources with a miniumum of effort.  Furthermore,
each package specified in the catalog is versioned.  This allows Inca to
automatically distribute reporter code updates such as bug fixes.  As such,
Inca administrators maintaining repositories need to be careful to ensure
their updates are tested and work.
% XXX Check with Jim on that

% We have a lot of reporters ready to be picked 
The Inca team publishes a reporter repository that contains 143 reporters
developed and tested for TeraGrid.  Most reporters are either version
reporters that collect version information from a softare package and
serve as a most basic unit test, unit test reporters that run a more involved
unit test, or performance benchmark reporters.  The unit and version
reporters cover software such as Grid middleware, compilers, math libraries,
data tools, and visualization tools.  The performance reporters available
currently measure data transfer and execute Grid benchmarks as described in
Section~\ref{grasp}.

\SubSection{Inca administration tool (incat)}
%\begin{figure}[htb]
%  \centering
%  \mbox{\epsfig{file=incat.eps, width=\columnwidth}}
%  \caption{\label{arch_fig} Incat .}
%\end{figure}

% Incat is interface Inca admin uses to configure reporters to resources
% introduce series here; why suites are important It is designed to make the
% effort of configuring and maintaining 100s series on resources easilty
The Inca administrative tool (incat) is a GUI implemented in Java Swing an
Inca administrator uses to configure user-level Grid monitoring on their
resources.  Incat allows an Inca administrator to choose which resources to
monitor and which reporters to deploy to those resources.  The configuration
is stored in a XML file and sent to the agent which handles the implementation
(as described in the next section).  The Inca administrator can reload the
configuration at any point and make updates.  Incat provides a number of
conveniences that enable a large number of results to be managed and collected
with a minimum effort.

Once an Inca administrator enters the location of one more reporter
repositories, incat will load and display the reporters available from them.
For each reporter, the Inca administrator can specify the resources to run on,
input arguments, the runtime environment, the frequency of execution, resource
limits, and email notifications.  The reports that a reporter produces on a
resource when executed with specific set of input arguments and runtime
environment are known as a \emph{report series} (or \emph{series} for short).
Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
produce one report series when executed with host tg-login.sdsc.edu and
another report series when executed with dslogin.sdsc.edu.  A set of related
series can be grouped into \emph{suites} and shared across other Inca
deployments.  For example, there could be a Globus suite or a data transfer
performance suite.  Suites can also be useful to determine interoperability
among Grids or to determine whether an application's requirements are being
fulfilled on a Grid.

% Resource information organized to make it easier to maintain
For each monitored resource, an Inca administrator selects an access method
(SSH or Globus) to access the resource and start monitoring there (described
in Sections~\ref{agent} and ~\ref{rm}).  Resources can also be grouped
together and referenced in the series configuration.  This facilitates the
process of executing the same series on multiple resources.  Furthermore,
attributes called \emph{macros} can be attached to resources and resource
groups and similarly be referenced in the series configuration (i.e., inputs
and runtime environment).  For example, it is useful to have a macro called
'jobmanager' since the batch system is likely to differ from one machine to
the next.  A resource macro can also have multiple values in which case the
series will be executed on the resource once for each macro value.  The
benefit of resource groups and macros is that when a reporter is executed on a
resource multiple times with different input arguments, it can be represented
succintly.  Similarly, when a resource attribute is changed, it only has to be
changed in one place and then every series that references it will be updated
as well.  This makes the initial configuration and maintenance easier on the
Inca administrator and less error prone.

\SubSection{Agent}

The Inca agent is a server that implements the configuration specified by the
Inca administrator.  When it receives a configuration file from the Inca
administrator, it will determine which reporters should be executed on each
resource by expanding the resource macros and groups; it then stores the
expanded configuration information in the depot.  The agent stages and
launches an Inca component, called a reporter manager (described in the
following subsection), on each resource using either SSH or Globus.  Once a
reporter manager contacts its agent, the agent transmits the reporters to
execute along with their dependencies and a suite that contains their series
configuration and schedule of execution.  As an Inca administrator makes
updates to the configuration, the agent will push out new reporters and/or
suite changes to each of the effected resources.

To maintain the Inca deployment, the agent regularly pings the reporter
managers on each resource in order to detect when a reporter manager has
failed so it can be restarted.  For example, if a resource goes down for a
planned maintenance, the agent will attempt to restart the reporter manager
(by default every hour) until it succeeds.  The agent also maintains a local
cache of reporters and their dependencies; it periodically checks the
repositories for updates every 4 hours by default and automatically
distributes them to the reporter managers (if the latest version is desired).  
The agent is implemented in Java.

% myproxy

\SubSection{Reporter Manager}

@@

@@

% Description and Requirements - Describe CTSS
Requirements for user-level Grid monitoring on TeraGrid initially included the
validation and verification of CTSS on each resource.  As described in the
introduction, CTSS was designed to
allow users to more easily run Grid jobs across its distributed, heterogeneous
resources.  CTSS version 3 (CTSSv3) is available from all TeraGrid compute
resources and is comprised of approximately 30 software packages that provide
Grid tools and services (e.g., Globus, GSI-SSH, MyProxy), data management
tools (e.g., SRB, HDF5), and applications tools (e.g., MPICH, GCC).
Inca was originally
deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
to collect job usage information from Globus 2 GRAM logs and to detect expired
host and CA certificates and CA CRLs.

% Usage of Inca - Describe reporters, configuration, and deployment.  Figure.
To provide user-level monitoring of CTSSv3, a number of version and unit
test reporters were developed to test the software packages in CTSS.
Currently, there are 56 such reporters executing an average of 109 series on
each of TeraGrid's 18 resources.  They include 48 all-to-all tests (GSI-SSH,
GRAM, and GridFTP), 20 Grid-related tests, 28 data-related tests, 30
application tool-related tests, and 2 security-related tests.  
Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 deployment
configuration.  The
agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
at SDSC on inca.sdsc.edu.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.6]{tg-deploy.eps}
  \caption{TeraGrid's Inca 2 Deployment.}
  \label{tg_deploy_fig}
\end{figure}

% Results - Consumer view of CTSS, security, etc.
TeraGrid currently has six status pages to display the Inca monitoring
information: a summary of CTSSv3 test failures, a detailed grid of CTSSv3 test
results, a page showing grid job
usage, results for security tests, results for secure mds tests, and a list of
all running reporters.

Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed CTSSv3 
test result
page.  CTSSv3 software packages are listed along the column and TeraGrid
resources (anonymized) in the header rows.  Test results for each package and
resource are shown in the table body rows.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.4]{status-page.eps}
  \caption{Portion of the TeraGrid CTSSv3 detailed status page with the
  resources anonymized.}
  \label{status_page_fig}
\end{figure}

\SubSection{GrASP}

@@

% Describe GrASP probes

\subsubsection{Usage of Inca}

% Used to deploy GrASP probes to Grids.  Probes wrapped as reporters (maybe
% right in future as though we already included GrASP as a dependency cause
% it should be done by June.

@@

% A paper.  Interesting that error messages were important.  Predictions?

\SubSection{Other uses}
~\newpage
%------------------------------------------------------------------------- 
\Section{Future Work}

\SubSection{Graphing and Summary Statistics}

\SubSection{Knowledge Base}

\SubSection{Fault Tolerance}
~\newpage

>>>>

% Standard "Grids are good" intro paragraph.  But are complex.  
Grid systems provide unified and coherent access to distributed computing,
data storage and analysis, instruments, and other resources.  These systems
require the careful coordination of software packages, services, and
configurations across multiple, heterogeneous resources.  The TeraGrid
project~\cite{teragrid}, for example, manages the coordination of software and
services by deploying and monitoring a common user environment across
distributed, heterogeneous resources. The organization of TeraGrid software
and services is referred to as the Coordinated TeraGrid Software and Services
(CTSS).  TeraGrid's software and services uniformity simplifies access to its
resources, which consist of more than 102 teraflops of compute capability and
more than 15 petabytes of online storage, all interconnected by a network that
can transfer a terabyte of data in under 10 minutes.

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains 
requiring a significant amount of coordination.  This is typically performed by
a group of Grid administrators or operators who consider local site policies and
resource heterogeneity
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured.  
Each site's system administrators, who are not necessarily Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise inconsistencies between the resources arise that either
inconvenience the user or prevent them from using particular resources
together.  A second challenge is that failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs.  In order to address these challenges,
Grid monitoring can be used to detect such problems leading to a more
stable and dependable Grid infrastructure.

% What types of Grid monitoring are around and what the limitations are
One approach to monitoring Grids, used by tools such as
MonALISA~\cite{monalisa} and GridICE~\cite{gridice}, is to aggregate and
display data from existing cluster or system administrator monitoring tools
such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, or
Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
resources where low-level host statistics and queue information can be
examined.  This type of monitoring information is useful for showing the
utilization of Grid resources but it does not provide the type of
high-level monitoring needed to detect user problems within the Grid
infrastructure, such as incompatible software versions.

@@

% Implements user-level Grid monitoring and who it benefits
Inca 2 is a system that provides user-level monitoring of Grid functionality
and performance described in the previous section.  It was designed to be
general, flexible, scalable, and secure in addition to being easy to deploy
and maintain.  Inca benefits Grid operators who oversee the day-to-day
operation of a Grid; system administrators who provide and manage resources;
and users who run applications on a Grid.  The key features of Inca 2 are
listed below.  The '*' after the feature description indicates it is a new
feature of Inca 2 while no '*' indicates an improvement to an Inca 1 feature.

@@

\item Collects a wide variety of user-level monitoring results (e.g., simple
test data to more complex performance benchmark output).

\item Captures the context of a test or benchmark as it executes (e.g.,
executable name, inputs, source host, etc.) so that system administrators have
enough information to understand the result and can troubleshoot system
problems without having to know the internals of Inca.

\item Eases the process of writing tests or benchmarks and deploying them into
Inca installations.

\item Provides means for sharing tests or benchmarks with other Inca 
users in order to promote sharing of each other's expertise. *

\item Easily adapts to new resources and monitoring requirements in order to
facilitate maintenance of a running Inca deployment.

\item Stores and archives monitoring results (especially any error messages) 
in order to understand the behavior of a Grid over time. The results
are available through a flexible querying interface.

\item Securely manages short-term proxies for testing of Grid services using
MyProxy~\cite{myproxy}. *

\item Measures the system impact of tests and benchmarks executing on
the monitored resources in order to tune their execution frequency to
reduce the impact on the resources. *

\end{enumerate}

\noindent The following section describes how the above features are
implemented.

@@

\begin{figure*}[tbp]
  \centering
  \mbox{\epsfig{file=arch.eps, width=.7\textwidth}}
  \caption{\label{arch_fig} Inca architecture.}
\end{figure*}

@@

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}[tbp]
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) an output sample.}
\end{figure}

An Inca reporter is an executable program that tests or measures some aspect
of a system or installed software.   Reporter executables are designed to be
easy to produce and can be run outside of the Inca system (e.g., by a system
administrator).  A reporter should be written using the user-level
monitoring guidelines described in the introduction and could be a simple
Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
support certain command line options and produce an XML document or
\emph{report}
according to the Inca reporter schema.  The goal of the reporter schema is to
accommodate multiple types of data and to capture enough information about the
reporter execution to diagnose any detected failures.  The reporter schema
consists of the following elements:

@@

% What are repositories and their key features
Reporter repositories are collections that consist of reporters, required
packages and libraries (including the Perl APIs described in the previous
section), and a catalog file.  Repository contents are accessible using a URL
and designed to be shared across multiple Inca deployments.  The catalog file
follows APT's Packages.gz~\cite{apt} format and thus tar.gz dependencies such
as non-standard Perl APIs or source code can be added to reporter catalog
entries.  Inca will then automatically deploy tar.gz dependencies into a
subdirectory of its installation (more in Section~\ref{agent}).  This enables
reporters to be deployed to resources with a minimum of effort.  Furthermore,
each package specified in the catalog is versioned.  This allows Inca to
automatically distribute reporter code updates such as bug fixes.  As such,
Inca administrators maintaining repositories need to be careful to ensure
their updates are tested and work.

% We have a lot of reporters ready to be picked 
The Inca team publishes a reporter repository that contains 143 reporters
developed and tested for TeraGrid.  Most reporters are either version
reporters that collect version information from a software package and
serve as a most basic unit test, unit test reporters that run a more involved
unit test, or performance benchmark reporters.  The unit and version
reporters cover software such as Grid middleware, compilers, math libraries,
data tools, and visualization tools.  The performance reporters available
currently measure data transfer and execute Grid benchmarks as described in
Section~\ref{grasp}.

\SubSection{Inca administration tool (incat)}

\begin{figure*}[tbp]
  \centering
  \mbox{\epsfig{file=incat.eps, width=\textwidth}}
  \caption{\label{incat_fig} Screenshot of incat that shows the reporters
  and their attributes available from the provided reporter repository.}
\end{figure*}

% Incat is interface Inca admin uses to configure reporters to resources
% introduce series here; why suites are important It is designed to make the
% effort of configuring and maintaining 100s series on resources easilty
The Inca administrative tool (incat) is a GUI implemented in Java Swing that an
Inca administrator uses to configure user-level Grid monitoring on their
resources.  Incat allows an Inca administrator to choose which resources to
monitor and which reporters to deploy to those resources.  The configuration
is stored in a XML file and sent to the agent, which handles the implementation
(as described in the next section).  The Inca administrator can reload the
configuration at any point and make updates.  Incat provides a number of
conveniences that enable a large number of results to be managed and collected
with a minimum effort.

To begin reporter configuration, the Inca administrator enters the location of
one more reporter repositories and incat will load and display the reporters
available from them as shown in Figure~\ref{incat_fig}.
For each reporter, the Inca administrator can specify the resources to run on,
input arguments, the runtime environment, the frequency of execution, resource
limits, and email notifications.  The reports that a reporter produces on a
resource when executed with specific set of input arguments and runtime
environment are known as a \emph{report series} (or \emph{series} for short).
Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
produce one report series when executed with host 'tg-login.sdsc.edu' and
another report series when executed with 'dslogin.sdsc.edu'.  A set of related
series can be grouped into \emph{suites} and shared across other Inca
deployments, e.g.,  a Globus suite or a data transfer
performance suite.  Suites can also be useful to determine interoperability
among Grids or to determine whether an application's requirements are being
fulfilled on a Grid.

% Resource information organized to make it easier to maintain
For each monitored resource, an Inca administrator selects an access method
(SSH or Globus) to access the resource and start monitoring there (described
in Sections~\ref{agent} and ~\ref{rm}).  Resources can also be grouped
together and referenced in the series configuration.  This facilitates the
process of executing the same series on multiple resources.  Furthermore,
attributes called \emph{macros} can be attached to resources and resource
groups and similarly be referenced in the series configuration (i.e., inputs
and runtime environment).  For example, it is useful to have a macro called
'jobmanager' since the batch system is likely to differ from one machine to
the next and multiple tests will require its value.  A resource macro can also
have multiple values in which case the series will be executed on the resource
once for each macro value.  The
benefit of resource groups and macros is that when a reporter is executed on a
resource multiple times with different input arguments, it can be represented
succinctly.  Similarly, when a resource attribute is changed, it only has to be
changed in one place and then every series that references it will be updated
as well.  This makes the initial configuration and maintenance easier on the
Inca administrator and less error prone.

\SubSection{Agent}
\label{agent}

The Inca agent is a server that implements the configuration specified by the
Inca administrator.  When it receives a configuration file from the Inca
administrator, it will determine which reporters should be executed on each
resource by expanding the resource macros and groups; it then stores the
expanded configuration information in the depot.  The agent stages and
launches an Inca component, called a reporter manager (described in the
following subsection), on each resource using either SSH or Globus.  Once a
reporter manager contacts its agent, the agent transmits the reporters to
execute along with their dependencies and a suite that contains their series
configuration and schedule of execution.  As an Inca administrator makes
updates to the configuration, the agent will push out new reporters and/or
suite changes to each of the affected resources.

To further manage the Inca deployment, the agent regularly pings the reporter
managers on each resource in order to detect when a reporter manager has
failed so it can be restarted.  For example, if a resource goes down for a
planned maintenance, the agent will attempt to restart the reporter manager
(by default every hour) until it succeeds.  The agent also maintains a local
cache of reporters and their dependencies; it periodically checks the
repositories for updates every 4 hours by default and automatically
distributes them to the reporter managers (if the latest version is desired).  
The agent is implemented in Java.

\SubSection{Reporter Manager}
\label{rm}

@@

% depot designed to support mirror depot or hierchical support
% coordinating Inca deployments

@@

% Description and Requirements - Describe CTSS
Requirements for user-level Grid monitoring on TeraGrid initially included the
validation and verification of CTSS on each resource.  As described in the
introduction, CTSS was designed to
allow users to more easily run Grid jobs across its distributed, heterogeneous
resources.  CTSS version 3 (CTSSv3) is available from all TeraGrid compute
resources and contains approximately 30 software packages that provide
Grid tools and services (e.g., Globus, GSI-SSH, MyProxy), data management
tools (e.g., SRB, HDF5), and applications tools (e.g., MPICH, GCC).
Inca was originally
deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
to collect job usage information from Globus 2 GRAM logs and to detect expired
host and CA certificates and CA CRLs.

% Usage of Inca - Describe reporters, configuration, and deployment.  Figure.
To provide user-level monitoring of CTSSv3, a number of version and unit
test reporters were developed to test the software packages in CTSS.
Currently, there are 56 such reporters executing an average of 109 series on
each of TeraGrid's 18 resources.  They include 48 all-to-all tests (GSI-SSH,
GRAM, and GridFTP), 20 Grid-related tests, 28 data-related tests, 30
application tool-related tests, and 2 security-related tests.  The TeraGrid
Inca configuration makes extensive use of macros and resource groups and
currently uses 80 series and 82 resource macros to manage the total of 1928
series executing on TeraGrid resources.
Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 deployment
configuration.  The
agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
at SDSC on inca.sdsc.edu.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{tg-deploy.eps}
  \caption{TeraGrid's Inca 2 Deployment.}
  \label{tg_deploy_fig}
\end{figure}

% Results - Consumer view of CTSS, security, etc.
TeraGrid currently has six status pages to display the Inca monitoring
information: a summary of CTSSv3 test failures, a detailed grid of CTSSv3 test
results, a page showing grid job
usage, results for security tests, results for secure MDS tests, and a list of
all running reporters.

Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed grid of
CTSSv3 test results
page.  CTSSv3 software packages are listed along the column and TeraGrid
resources (anonymized) in the header rows.  Test results for each package and
resource are shown in the table body rows.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{status-page.eps}
  \caption{Portion of the TeraGrid CTSSv3 detailed status page with the
  resources anonymized.}
  \label{status_page_fig}
\end{figure}

\SubSection{GrASP}
\label{grasp}

@@

% Describe GrASP probes
The Grid Assessment Probes (GrASP)~\cite{grasp} are designed to 
serve as simple grid application kernel exemplars as well as a 
set of diagnostic tools. They test and measure performance of 
basic grid functions including file transfers, remote execution, 
and Grid Information Services response.  There are two basic probes: i.  The
circle probe takes a 100 MB file and passes it in a ring through a given set
of grid nodes, measuring transfer time at each step.  ii.  The gather probe
transfers a 100 MB file from some number of source nodes to a compute node,
runs a computation through the job queue on the compute resource and then
transfers a 100 MB file to a single destination node.  The transfer of the
first set of files is executed in parallel.  Once again all tranfers times, as
well as compute and queue times are recorded.

The GrASP probes yield useful data on the performance and reliability of the
grid infrastructure that they are run on.  In order for the data gathered to
be useful, it must gathered repeatedly over time and stored in a manner
appropriate for querying.  In addition to storing the measurements available
we also required that any error messages encountered be stored as well.    
In order to
fulfill the last 2 requirements we deployed the GrASP probes as reporters
within the Inca framework.

The GrASP probes have been written to follow the specifications of an Inca
reporter.  Porting the original code to follow the specifications proved to be
trivial.  Inca was also used to store all of the GrASP data and related error
messages.

\begin{figure}[tbp]
  \centering
  \mbox{\epsfig{file=errorHistogramTG.eps, width=\columnwidth}}
  \caption{\label{errorHist_fig} Histogram of Error Messages Encountered.}
\end{figure}

@@

GrASP, using Inca, was deployed on TeraGrid and Geon for a period of over 6
months.  The data gathered during that period yielded a paper, Measuring the
Performance and Reliability of Production Computational Grids ~\cite{grasp2}.
By the running of the GrASP probes over such an extended period of time
we were able to identify a recurring Globus 2 bug.  Figure ~\ref{errorHist_fig} shows the types (shortened) and number of system errors that were detected while executing the
benchmark during the GrASP deployment on TeraGrid in 2005. The highest occurring
error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
the Globus 2 GRAM server.  We were also able to predict the
execution time of Preco, a Grid application run on the TeraGrid within 12\% (excluding setup and cleanup time).

\SubSection{Other Uses}

Other Inca users include the European DEISA Grid and the UK National Grid
Service (NGS).  Similar to TeraGrid, DEISA uses Inca to verify their Common
Production Environment (DCPE) across their 11 heterogenous resources.  They
currently have 40 version reporters to verify each of the packages included in
DCPE.  In addition, they have unit reporters for the DEISA Applications Test
Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
party application.  DEISA is currently using Inca 1 and will transition to
Inca 2 in the next few months.

NGS currently has Inca 2 deployed on 8 resources to verify their Grid services 
and compilers.  They have wrapped the GITS~\cite{gits} tests using a new
API developed by the GITS developer.  The GITS reporters include 17 tests 
that verify Globus and GSI-SSH functionality such as executing small job
submissions and data transfers.  NGS also has 12 tests for their compilers and
utilize 2 security reporters from the Inca repository.

%------------------------------------------------------------------------- 
\Section{Future Work}

In order to improve problem detection and diagnosis for system administrators,
we plan to enhance the data consumer with graph rendering and statistical
analysis capabilities.  This will improve troubleshooting capabilities by
allowing errors to be understood in a historical context.  It will also enable
summary displays analogous to those generated by Web page statistics packages
like Webalizer~\cite{webalizer} that provide a number of useful "Top"
statistics.  We expect feedback from TeraGrid and other Inca users on the
exact types of statistics and graphs that will prove to be most useful.  Our
goal is to offer a default set of statistics and graphs that can be used out
of the box and provide the capability to add others.

Also in order to make it easier for system administrators to troubleshoot
problems, we plan to enhance Inca with a knowledge base that can be used to
suggest solutions to problems (or point to known bugs if there is no solution
available).  The knowledge base would be populated by solutions provided by
system administrators, and the content would be self-moderated in order to
improve its quality (by voting or adding comments to each other's
contributions).  This knowledge base represents a potentially vital resource
for system administrators and provides a forum to share each other's
invaluable experience and skills.

Finally, we plan to improve the fault tolerance of Inca by enhancing the
reporter manager so that it caches reports locally if it is unable to
contact the depot or sends reports to a backup depot if one is available.
The agent will similarly be enhanced to cache configuration changes locally or
send configuration to a backup depot if one is available in case of a depot
failure.
